%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Mayuresh Naidu} \\ \vspace{1pt}
    Toronto, ON M4R 0A4 \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 437-733-3495 ~ \href{mailto:mayureshnaiduu@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{mayureshnaiduu@gmail.com}} ~ 
    \href{https://linkedin.com/in/mayuresh-naidu-233802204/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/mayuresh-naidu}}  ~
    \href{https://github.com/}{\raisebox{-0.2\height}\faGithub\ \underline{github.com/meiyo99}}
    \vspace{-8pt}
\end{center}


%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item\small Web Development
                \item Software Methodology
                \item Data Structures
                \item Database Systems
                \item Front-End Frameworks
                \item RESTful API 
                \item Systems Programming
                \item UI/UX Design 
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Take5 Digital}{June 2024 -- August 2024}
      {UX Developer Intern}{London, ON}
      \resumeItemListStart
        \resumeItem{Contributed to the redesign of a client-facing website, focusing on improving layout structure, applying modern design principles, and enhancing user experience.}
        \resumeItem{Participated in agile workflows, including weekly standups and design review meetings, collaborating with cross-functional team members to align design strategies with user needs.}
        \resumeItem{Contributed creative input to design decisions, refining both aesthetic and functional elements based on feedback and testing.}
        \resumeItem{Gained hands-on experience working on a live web project, strengthening front-end development, UX design, and collaborative communication skills.}
    \resumeItemListEnd

    \resumeSubheading
      {GeBBS Healthcare}{Sep 2022 -- Sep 2023}
      {Software Engineer}{Mumbai, India}
      \resumeItemListStart
        \resumeItem{Collaborated with cross-functional teams to align design goals, conduct research, conduct design reviews, create prototypes, and conduct user testing sessions.}
        \resumeItem{Used finalized designs to develop responsive websites using front-end frameworks such as React.js, ensuring cross-browser compatibility.}
        \resumeItem{Maintained clear documentation, communicated design rationale, conducted iterative testing, and collaborated within Agile frameworks to resolve design-development issues and ensure continuous improvement.}
      \resumeItemListEnd
    
  \resumeSubHeadingListEnd
\vspace{-16pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-5pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Slot Machine} $|$ \emph{Python}}{}
          \resumeItemListStart
            \resumeItem{Developed a text-based slot machine game using Python, incorporating betting mechanics, balance tracking, and randomized symbol generation on a 3x3 grid.}
            \resumeItem{Implemented logic to calculate winnings based on predefined symbol frequencies and payout values, enhancing understanding of probability and control flow.}
            \resumeItem{Designed a user-driven game loop with input validation and dynamic feedback, improving console-based interaction and user experience.}
          \resumeItemListEnd
          \vspace{-13pt}
      \resumeProjectHeading
          {\textbf{PlantPal Plant Care} $|$ \emph{HTML, CSS, JQuery}}{}
          \resumeItemListStart
            \resumeItem{Developed a plant management web application enabling users to add, delete, and customize plant entries with species-specific details and care information.}
            \resumeItem{Implemented search functionality and interactive task tracking using a visual calendar to display and mark watering reminders.}
            \resumeItem{Utilized browser storage (local/session) to ensure data persistence and enhance user experience without requiring a backend.}
          \resumeItemListEnd 
          \vspace{-13pt}
          \resumeProjectHeading
          {\textbf{BrickMMO Applications} $|$ \emph{PHP, JavaScript}}{}
          \resumeItemListStart
            \resumeItem{Proposed and designed advanced search, filter, and sort functionalities to enhance discoverability and usability of GitHub repositories.}
            \resumeItem{Conceptualized contributor insights and activity visualizations to improve transparency and engagement within the developer community.}
            \resumeItem{Focused on transforming a static listing into an interactive, user-centric platform through feature ideation grounded in real-world use cases.}
          \resumeItemListEnd 
    \resumeSubHeadingListEnd
\vspace{-15pt}


%

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart

  \resumeSubheading
      {Humber Polytechnic}{Jan 2025 -- Dec 2025}
      {Post-Graduate Certificate in Web Development}{Etobicoke, ON}

  \resumeSubheading
      {Conestoga College}{Jan 2024 -- Dec 2024}
      {Post-Graduate Certificate in Web Development}{Etobicoke, ON}
      
    \resumeSubheading
      {MIT ADT University}{2017 -- 2021}
      {Bachelor of Technology in Computer Science}{Pune, India}
  \resumeSubHeadingListEnd

  
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages:} Python, PHP, C\#, HTML/CSS, JavaScript, SQL \\
     \textbf{Developer Tools}{: VS Code, Git, Docker, Figma, Framer} \\
     \textbf{Technologies/Frameworks}{: .Net, React, Express, Node.js, GitHub, MongoDB} \\
    }}
 \end{itemize}
 \vspace{-16pt}


%-----------INVOLVEMENT---------------
\section{Volunteering / Extracurricular}
    \resumeSubHeadingListStart
        \resumeSubheading{Collision Conference}{June 2024}{Volunteer}{Toronto}
            \resumeItemListStart
                \resumeItem{Supported logistics for a tech event hosting 40,000+ attendees, gaining experience in high-pressure technical environments.}
                \resumeItem{Triaged support requests efficiently while maintaining a high-quality customer experience.}
                \resumeItem{Coordinated across teams and provided on-site troubleshooting and support, enhancing adaptability and communication.}
            \resumeItemListEnd
        
    \resumeSubHeadingListEnd


\end{document}
